Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-15 paper/paper.qmd
Updated wording of abstract

---
title: "Differences in Homicide Case Information Indicates Why Justice is Not Served"
subtitle: "An analysis of solved and unsolved homicides from 2010 to 2017 in one of the United States' 2 largest cities, Chicago and Los Angeles"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/unsolved-murders](https://github.com/moonsdust/unsolved-murders)."
date: today
date-format: long
abstract: "Despite Chicago Mayor Brandon Johnson announcing in 2024 that the Chicago Police Department had the highest homicide clearance rate of 54% in years, homicide clearance rates across the United States (US) have been decreasing since 1980, with more homicides going unsolved. This paper looks at patterns of homicide case information with the case resolution from 2010 to 2017 in two of the largest cities in the United States, Chicago and Los Angeles. We found that unsolved homicides are more likely to occur in Chicago compared to Los Angeles, and the majority of unsolved homicide victims are Black or Hispanic and are male. These findings can inform the public and US police departments of populations more vulnerable to having unsolved cases however further investigation is needed on the investigators involved in each unsolved homicide case."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Differences in Homicide Case Information Indicates Why Justice is Not Served"
subtitle: "An analysis of solved and unsolved homicides from 2010 to 2017 in one of the United States' 2 largest cities, Chicago and Los Angeles"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/unsolved-murders](https://github.com/moonsdust/unsolved-murders)."
date: today
date-format: long
abstract: "Despite Chicago Mayor Brandon Johnson announcing in 2024 that the Chicago Police Department had the highest homicide clearance rate of 54% in years, homicide clearance rates across the United States (US) have been decreasing since 1980, with more homicides going unsolved. This paper looks at patterns of homicide case information with the case resolution from 2010 to 2017 in two of the largest cities in the United States, Chicago and Los Angeles. We found that unsolved homicides are more likely to occur in the middle and later half of the year and in Chicago compared to Los Angeles with the majority of victims being Black or Hispanic males. These findings can inform the public and US police departments of populations more vulnerable to having unsolved cases however further investigation is needed on the investigators involved in each unsolved homicide case."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---
